Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-08-22 paper.tex
retoques de escrita

\begin{abstract}
In this study, we demonstrate a remarkably stable activity in human interaction networks. The activity along time and topology evolution were investigated in email lists by considering window sizes from 50 to 10,000 messages, which were made to slide and generate snapshots of the network in a timeline. Notably, the activity in timescales ranging from seconds to months, is practically the same for all lists. The activity of participants followed the expected scale-free behavior, thus allowing us to establish three classes of vertices by comparing against the Erd\"os-R\'enyi model, namely hubs, intermediary and peripheral vertices. The relative size of these three sectors did not vary with time and was essentially the same for all email lists. Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and the remainder are peripheral vertices. The metrics that contribute most to the dispersion of participants in the topological measures space are centrality measurements (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient. Similar results for the distribution of participants in the three categories and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participa.br. Consistent with expectations from the literature, these properties may be general for human interaction networks, which has important implications in establishing a typology based on objective, quantitative criteria.
\end{abstract}

@@

\section{Methods}\label{sec:carac}
The email lists and the networks generated from them were characterized using five procedures, namely: 1) statistics of activity along time, in scales from seconds to years; 2) sectioning of the networks in hubs, intermediary and peripheral vertices; 3) dispersion of basic topological metrics; 4) iterative visualization and data inspection.
Each of these procedures are described below.

>>>>

\begin{abstract}
In this study, we demonstrate a remarkably stable activity in human interaction networks. The activity along time and topology evolution were investigated in email lists by considering window sizes from 50 to 10,000 messages, which were made to slide and generate snapshots of the network in a timeline. Notably, the activity in timescales, ranging from seconds to months, is practically the same for all lists. The activity of participants followed the expected scale-free behavior, thus allowing us to establish three classes of vertices by comparing against the Erd\"os-R\'enyi model, namely hubs, intermediary and peripheral vertices. The relative size of these three sectors did not vary with time and was essentially the same for all email lists. Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and the remainder are peripheral vertices. The metrics that contribute most to the dispersion of participants in the topological measures space are centrality measurements (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient. Similar results for the distribution of participants in the three categories and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participa.br. Consistent with expectations from the literature, these properties may be general for human interaction networks, which has important implications in establishing a typology based on objective, quantitative criteria.
\end{abstract}

@@

\section{Methods}\label{sec:carac}
The email lists and the networks generated from them were characterized using four procedures, namely: 1) statistics of activity along time, in scales from seconds to years; 2) sectioning of the networks in hubs, intermediary and peripheral vertices; 3) dispersion of basic topological metrics; 4) iterative visualization and data inspection.
These procedures are described below.
